Weather vanes and runaways: Bow shocks across the HR diagram

### 2018-06-25 papers/Papers1234/app-dust-wave.tex
Add figure for the parallel inertia-confined dust wave

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/perp-bfield-dust-wave-inertia}
  \caption{Inertia-confined dust wave with perpendicular field}
  \label{fig:inertia-thB90}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/parallel-bfield-dust-wave-inertia}
  \caption{Dust wave formed by action of radiation forces on grains
    that are tightly coupled to a uniform parallel magnetic field.}
  \label{fig:inertia-thB0}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/perp-bfield-dust-wave-inertia}
  \caption{Dust wave formed by action of radiation forces on grains
    that are tightly coupled to a uniform perpendicular magnetic
    field.}
  \label{fig:inertia-thB90}
\end{figure}

For \(\theta\B = \ang{90}\), the guiding center is forced to move at a
constant speed in the \(x\) direction, so that \(x = -v_\infty t\), while
the motion in the \(y\) direction obeys the ODE:
\begin{equation}
  \label{eq:ode-perp-bfield}
  \frac{d^2 Y}{d X^2} = \frac{Y}{2 \left( X^2 + Y^2\right)^{3/2}} \ ,
\end{equation}
where \(X = x / R\starstar\) and \(Y = y / R\starstar\).  We have been
unable to find an analytic solution to this equation, but a numerical
solution is shown in Figure~\ref{fig:inertia-thB90}.

@@
